HW #4: Analyze real-world emissions data

### 2022-12-03 HW4/HW4.Rmd
fix hw4.3

But this does not wholly discount the benefit of I/M programs. In fact, I'd argue these programs (or at least the concept of them) are a good thing so long as equity can be addressed properly. Perhaps funds that would have gone to I/M programs could be used as a subsidy for low-income individuals to purchase more climate-friendly vehicles. Though this doesn't address the question of what to do with high-emitting vehicles directly, increasing the gas/diesel tax would discourage driving as much (lowering emissions), and then the excess funds could again be used as subsidies for low- to no-emitting vehicles.

>>>>

But this does not wholly discount the benefit of I/M programs. In fact, I'd argue these programs (or at least the concept of them) are a good thing so long as equity can be addressed properly. Perhaps, though, funds that would have gone to I/M programs could be better used as a subsidy for low-income individuals to purchase more climate-friendly vehicles. Though this doesn't address the question of what to do with high-emitting vehicles directly, increasing the gas/diesel tax would discourage driving as much (lowering emissions), and then the excess funds could again be used as subsidies for low- to no-emitting vehicles.
